Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2016-11-08 Paper.tex
In 4

\noindent Many traditional techniques have been proposed for the segmentation of
nuclei in histopathology images, ranging from simple background
subtraction and color threshold techniques \cite{Yuan2012} 
to much more
sophisticated approaches, such as marked point
processes\cite{Kulikova2012}. Many of these methods have been recently
reviewed \cite{irshad2014methods}.

@@

Alternative methods 
have arisen from the achieving Convolutional neural networks 
%\cite{lecun}, 
%in particular strong incentive rose with the very impressive 
%results that they achieved in the pascal voc challenge with 
%\cite{ImageNet}. 
Recent advances in deep neural networks, and in 
particular in their optimization have made them become the state-of-the-
art model for object recognition.  Deep neural network have also been 
used for 
semantic segmentation, where \cite{long2015fcn} use "de-
convolution layers" and up-sampling in order to identify and precisely 
locate objects within a picture. Different architecture arising from 
different intuition are also possible and have been applied in this paper.

>>>>

\noindent Many traditional techniques have been proposed for the segmentation of
nuclei in histopathology images, ranging from simple background
subtraction and color threshold techniques 
to much more
sophisticated approaches, such as marked point
processes\cite{Kulikova2012}. Many of these methods have been recently
reviewed \cite{irshad2014methods}.

@@

Alternative methods 
have arisen from the achieving Convolutional neural networks.
%\cite{lecun}, 
%in particular strong incentive rose with the very impressive 
%results that they achieved in the pascal voc challenge with 
%\cite{ImageNet}. 
Recent advances in deep neural networks, and in 
particular in their optimization have made them become the state-of-the-
art model for object recognition.  Deep neural network have also been 
used for 
semantic segmentation, where \cite{long2015fcn} use "de-
convolution layers" and up-sampling in order to identify and precisely 
locate objects within a picture. Different architecture arising from 
different intuition are also possible and have been applied in this paper.
